### 2012-01-20 docs/compilers/compilers.tex
update gfortran notes

Probably the best compilers for \maestro.  Versions 4.5 and 4.6 seem to work
really well and the debugging features are very reliable.

>>>>

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1 and 4.6.2 on Fedora (15 and 16) have a bug that 
shows up in multi-processor runs ({\tt toy\_convect} on 4 processors, for instance).
The symptom is a crash during initialization with the message that
``message sizes do not match across processes in the collective'' in a
{\tt parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue seems
to be a multiplication error in computing the size to allocate {\tt bxs}.
The bug is not present when you compile in debug mode, so it seems to be
related to optimization.
\end{itemize}

An added benefit of the gfortran compilers is that their debugging
features are very reliable.
